Population Differentiation Analysis

### 2017-08-02 doc/RMD/pop-diff.Rmd
add seed to poppr run

```{r geno-div, cache = TRUE, fig.width = 10, fig.height = 10, comment = NA}
ptab <- dat11cc %>% setPop(~Region) %>% poppr(sample = 999, total = FALSE)
```

```{r geno-div2, fig.width = 10, fig.height = 10, comment = NA}
ptab %>%
  arrange(desc(N), desc(MLG)) %>%
  mutate(Ia = case_when(
    !is.finite(p.Ia) ~ "-",
    p.Ia == 0.001 ~ paste0(round(Ia, 2), "*"),
    p.Ia <= 0.01  ~ paste0(round(Ia, 2), "-"),
    p.Ia <= 0.05  ~ paste0(round(Ia, 2), "~"),
    TRUE          ~ as.character(round(Ia, 2))
  )) %>%
  mutate(rbarD = case_when(
    !is.finite(p.rD) ~ "-",
    p.rD == 0.001 ~ paste0(round(rbarD, 2), "*"),
    p.rD <= 0.01  ~ paste0(round(rbarD, 2), "-"),
    p.rD <= 0.05  ~ paste0(round(rbarD, 2), "~"),
    TRUE          ~ as.character(round(rbarD, 2))
  )) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(N = paste(N, MLG, sep = " (") %>% paste0(")") %>% formatC()) %>%
  mutate(eMLG = paste(eMLG, SE, sep = " (") %>%  paste0(")") %>% formatC()) %>%
  rename(`*h*` = Hexp) %>%
  rename(`$E_5$` = E.5) %>%
  rename(`$I_A$` = Ia) %>%
  rename(`$\\lambda$` = lambda) %>%
  rename(`$\\bar{r}_d$` = rbarD) %>%
  select(-File, -MLG, -SE, -p.rD, -p.Ia) %>% 
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 1) %>%
  huxtable::set_align(huxtable::everywhere, -1, "right") %>%
  huxtable::set_col_width(c(1.1, 0.9, 1.3, 0.5, 0.5, 1.2, 0.7, 0.6, 0.6, 0.8)) %>%
  huxtable::print_md(max_width = 80)

ptab %>% 
  arrange(desc(N), desc(MLG)) %>% 
  write_csv(file.path(PROJHOME, "results/tables/genotype_diversity_table_region.csv"), col_names = TRUE)

>>>>

```{r geno-div, cache = TRUE, fig.width = 10, fig.height = 10, comment = NA}
set.seed(2017-08-02)
ptab <- dat11cc %>% setPop(~Region) %>% poppr(sample = 999, total = FALSE)
```

```{r geno-div2, fig.width = 10, fig.height = 10, comment = NA}
ptab %>%
  arrange(desc(N), desc(MLG)) %>%
  write_csv(file.path(PROJHOME, "results/tables/genotype_diversity_table_region.csv"), col_names = TRUE) %>%
  mutate(Ia = case_when(
    !is.finite(p.Ia) ~ "-",
    p.Ia == 0.001 ~ paste0(round(Ia, 2), "*"),
    p.Ia <= 0.01  ~ paste0(round(Ia, 2), "-"),
    p.Ia <= 0.05  ~ paste0(round(Ia, 2), "~"),
    TRUE          ~ as.character(round(Ia, 2))
  )) %>%
  mutate(rbarD = case_when(
    !is.finite(p.rD) ~ "-",
    p.rD == 0.001 ~ paste0(round(rbarD, 2), "*"),
    p.rD <= 0.01  ~ paste0(round(rbarD, 2), "-"),
    p.rD <= 0.05  ~ paste0(round(rbarD, 2), "~"),
    TRUE          ~ as.character(round(rbarD, 2))
  )) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(N = paste(N, MLG, sep = " (") %>% paste0(")") %>% formatC()) %>%
  mutate(eMLG = paste(eMLG, SE, sep = " (") %>%  paste0(")") %>% formatC()) %>%
  rename(`*h*` = Hexp) %>%
  rename(`$E_5$` = E.5) %>%
  rename(`$I_A$` = Ia) %>%
  rename(`$\\lambda$` = lambda) %>%
  rename(`$\\bar{r}_d$` = rbarD) %>%
  select(-File, -MLG, -SE, -p.rD, -p.Ia) %>% 
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 1) %>%
  huxtable::set_align(huxtable::everywhere, -1, "right") %>%
  huxtable::set_col_width(c(1.1, 0.9, 1.3, 0.5, 0.5, 1.2, 0.7, 0.6, 0.6, 0.8)) %>%
  huxtable::print_md(max_width = 80)
